Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-18 manu-draft.Rmd
nutrient flow ordination added

>>>>

```{r nutrientfloword, fig.cap = 'Ordination results comparing weekly summarized observations across all sampled locations for total nitrogen concentrations, chlorophyll-a concentrations, diatom cell concentrations, *Karenia brevis* cell concentrations, and cyanobacteria macroalgal abundances.  Ordination results are from non-metric multi-dimensional scaling performed on the 97.5th percentile values of observations in each week for each parameter.  Observations are grouped by month periods based on phytoplankton (diatoms or *K. brevis*) or macroalgal dominance.'}
knitr::include_graphics('figs/nutrientfloword.jpeg')
```
